### 2024-03-06 README/README.tex
Added LaTex files for README

% !TEX TS-program = pdflatex
% !TEX encoding = UTF-8 Unicode

% This is a simple template for a LaTeX document using the "article" class.
% See "book", "report", "letter" for other types of document.

\documentclass[11pt]{article} % use larger type; default would be 10pt

\usepackage[utf8]{inputenc} % set input encoding (not needed with XeLaTeX)

%%% Examples of Article customizations
% These packages are optional, depending whether you want the features they provide.
% See the LaTeX Companion or other references for full information.

%%% PAGE DIMENSIONS
\usepackage{geometry} % to change the page dimensions
\geometry{a4paper} % or letterpaper (US) or a5paper or....
% \geometry{margin=2in} % for example, change the margins to 2 inches all round
% \geometry{landscape} % set up the page for landscape
%   read geometry.pdf for detailed page layout information

% \usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent

%%% PACKAGES
\usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
%\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
% These packages are all incorporated in the memoir class to one degree or another...

%%% HEADERS & FOOTERS
\usepackage{fancyhdr} % This should be set AFTER setting up the page geometry
\pagestyle{fancy} % options: empty , plain , fancy
\renewcommand{\headrulewidth}{0pt} % customise the layout...
\lhead{}\chead{}\rhead{}
\lfoot{}\cfoot{\thepage}\rfoot{}

%%% SECTION TITLE APPEARANCE
\usepackage{sectsty}
\allsectionsfont{\sffamily\mdseries\upshape} % (See the fntguide.pdf for font help)
% (This matches ConTeXt defaults)

%%% ToC (table of contents) APPEARANCE
\usepackage[nottoc,notlof,notlot]{tocbibind} % Put the bibliography in the ToC
\usepackage[titles,subfigure]{tocloft} % Alter the style of the Table of Contents
\renewcommand{\cftsecfont}{\rmfamily\mdseries\upshape}
\renewcommand{\cftsecpagefont}{\rmfamily\mdseries\upshape} % No bold!

\usepackage{list_packages}
\usepackage{shortcuts}
\input{lmacros}

\newcommand{\abra}[1]{\langle #1 \rangle}
\newcommand{\dbra}[1]{\llbracket #1 \rrbracket}

\newcommand{\Opt}{\textsc{Opt}}
\newcommand{\BayesWC}{\textsc{BayesWC}}
\newcommand{\BayesPC}{\textsc{BayesPC}}

\newcommand{\defas}{\coloneq}

%%% END Article customizations

%%% The "real" document content comes below...

\title{[Artifact57] Robust Resource Bounds with\\
	Static Analysis and Bayesian Inference}
\author{Anonymous}
\date{\today} % Activate to display a given date or no date (if empty),
         % otherwise the current date is printed

\begin{document}
\maketitle

\input{getting_started_guide}
\input{step_by_step_instructions}

%\bibliographystyle{abbrvnat}
%\bibliography{}

\end{document}

### 2024-03-06 README/getting_started_guide.tex
Added LaTex files for README

% !TeX root = README.tex

\section{Getting Started Guide}

Our artifact, dubbed Hybrid Resource-Aware ML (RaML), is a program analysis tool
that takes in an OCaml program and infers its worst-case polynomial cost bound
using the technique Hybrid AARA described in the paper.

The artifact is wrapped inside the provided Docker image.
%
To run it, first install Docker according to the instructions at
\url{https://docs.docker.com/engine/install/}.
%
To see if Docker has been installed properly, run
\begin{verbatim}
$ docker --version
Docker version 25.0.3, build 4debf41
\end{verbatim}

Load and run the Docker image as follows:
\begin{verbatim}
$ docker load --input hybrid_aara.tar.gz
$ docker run -it --rm hybrid_aara
root@fca41f6f696d:/home/hybrid_aara/benchmark_suite/playground#
\end{verbatim}

In the initial working directory, we have a file \texttt{append.ml} that stores
the \texttt{append} function written in OCaml.
%
Given two inputs lists, the \texttt{append} function appends the first input to
the second one.
%
For each element in the first input that the function processes, it incurs a
cost ranging from 0.5 to 1.0.
%
Therefore, the worst-case cost bound of the function is $1.0 \cdot M$, where $M$
is the length of the first input list.

Hybrid RaML's executable is the file \texttt{/home/hybrid\_aara/raml/main}, and
its location has already been added to the \texttt{PATH} variable so that we can
call Hybrid RaML by running \texttt{main} anywhere in the filesystem.
%
Hybrid AARA (and its artifact Hybrid RaML) provides three types of hybrid
resource analysis: Hybrid \Opt{}, Hybrid \BayesWC{}, and Hybrid \BayesPC{}.

\subsection{Hybrid \Opt{}}

To perform Hybrid \Opt{} on the \texttt{append} function, run
\begin{verbatim}
# main stat_analyze ticks 1 -m append.ml append -config config_opt.json
\end{verbatim}
%
In the command, \texttt{stat\_analyze} means we want to perform Hybrid AARA
(instead of the conventional AARA).
%
The input \texttt{ticks} means the resource metric of our interest is the tick
metric (instead of heap memory, for example).
%
The number 1 means we want to infer degree-1 polynomial cost bounds.
%
The input \texttt{append.ml} specifies the input file name, and the input
\texttt{append} means we want to know a cost bound of the function
\texttt{append} (instead of other functions in the same file).
%
Finally, the input \texttt{config\_opt.json} specifies the configuration file
for Hybrid \Opt{}.

In the output printed on the stdout, you should find
\begin{verbatim}
== append :

[int list; int list] -> int list

Non-zero annotations of the argument:
    0.85  <--  ([::(*)], [])

Non-zero annotations of result:

Simplified bound:
    0.85*M
  where
    M is the number of ::-nodes of the 1st component of the argument
\end{verbatim}
%
It means that the cost bound inferred by Hybrid \Opt{} is $0.85 \cdot M$, where
$M$ is the first input's length.

\subsection{Hybrid \BayesWC{}}

Next, to perform Hybrid \BayesWC{}, run
\begin{verbatim}
# main stat_analyze ticks 1 -m append.ml append -config config_bayeswc.json
\end{verbatim}
where the configuration file is now \texttt{config\_bayeswc.json}, which
contains hyperparameters for Bayesian inference.
%
The analysis should finish in between 40 and 50 seconds.
%
Its output on the stdout should contain
\begin{verbatim}
== append :

  [int list; int list] -> int list

  Non-zero annotations of the argument:
(avg, std) = (   2.18047,   0.633256)  <--
                                         ([::(*)], [])
(avg, std) = ( 0.0101388,  0.0158341)  <--  ([], [::(*)])
(avg, std) = (         0,          0)  <--  ([], [])

  Non-zero annotations of result:
(avg, std) = (         0,          0)  <--
                                   [::(*)]
(avg, std) = (         0,          0)  <--  []

  Simplified bound:
     0.0101388*L + 2.18047*M
   where
     L is the number of ::-nodes of the 2nd component of the argument
     M is the number of ::-nodes of the 1st component of the argument
\end{verbatim}
%
Unlike Hybrid Opt{} that infers a single cost bound, Hybrid \BayesWC{} returns a
collection of cost bounds, which approximate their posterior distribution.
%
In the stdout, 0.0101388 is the average degree-one coefficient for the first
input in the posterior distribution, and likewise, 2.18047 is the average
coefficient for the second input.

\subsection{Hybrid \BayesPC{}}

To perform Hybrid \BayesPC{}, run
\begin{verbatim}
# main stat_analyze ticks 1 -m append.ml append -config config_bayespc.json
\end{verbatim}
using the configuration file \texttt{config\_bayespc.json}.
%
The analysis should terminate within 90 seconds.
%
The output printed on the stdout should contain
\begin{verbatim}
== append :

  [int list; int list] -> int list

  Non-zero annotations of the argument:
(avg, std) = (   2.03295,   0.228391)  <--  
                                         ([::(*)], [])
(avg, std) = (  0.281939,   0.146543)  <--  ([], [::(*)])
(avg, std) = (  0.164309,  0.0824471)  <--  ([], [])

  Non-zero annotations of result:
(avg, std) = (         0,          0)  <--  
                                   [::(*)]
(avg, std) = (         0,          0)  <--  []

  Simplified bound:
     0.164309 + 0.281939*L + 2.03295*M
   where
     L is the number of ::-nodes of the 2nd component of the argument
     M is the number of ::-nodes of the 1st component of the argument
\end{verbatim}
where \texttt{0.164309 + 0.281939*L + 2.03295*M} contains the average
coefficients.

### 2024-03-06 README/step_by_step_instructions.tex
Added LaTex files for README

--- 2024-03-06 README/getting_started_guide.tex
@@
 
-\section{Getting Started Guide}
-
-Our artifact, dubbed Hybrid Resource-Aware ML (RaML), is a program analysis tool
-that takes in an OCaml program and infers its worst-case polynomial cost bound
-using the technique Hybrid AARA described in the paper.
-
-The artifact is wrapped inside the provided Docker image.
-%
-To run it, first install Docker according to the instructions at
-\url{https://docs.docker.com/engine/install/}.
-%
-To see if Docker has been installed properly, run
-\begin{verbatim}
-$ docker --version
-Docker version 25.0.3, build 4debf41
-\end{verbatim}
-
-Load and run the Docker image as follows:
-\begin{verbatim}
-$ docker load --input hybrid_aara.tar.gz
-$ docker run -it --rm hybrid_aara
-root@fca41f6f696d:/home/hybrid_aara/benchmark_suite/playground#
-\end{verbatim}
-
-In the initial working directory, we have a file \texttt{append.ml} that stores
-the \texttt{append} function written in OCaml.
-%
-Given two inputs lists, the \texttt{append} function appends the first input to
-the second one.
-%
-For each element in the first input that the function processes, it incurs a
-cost ranging from 0.5 to 1.0.
-%
-Therefore, the worst-case cost bound of the function is $1.0 \cdot M$, where $M$
-is the length of the first input list.
-
-Hybrid RaML's executable is the file \texttt{/home/hybrid\_aara/raml/main}, and
-its location has already been added to the \texttt{PATH} variable so that we can
-call Hybrid RaML by running \texttt{main} anywhere in the filesystem.
-%
-Hybrid AARA (and its artifact Hybrid RaML) provides three types of hybrid
-resource analysis: Hybrid \Opt{}, Hybrid \BayesWC{}, and Hybrid \BayesPC{}.
-
-\subsection{Hybrid \Opt{}}
-
-To perform Hybrid \Opt{} on the \texttt{append} function, run
-\begin{verbatim}
-# main stat_analyze ticks 1 -m append.ml append -config config_opt.json
-\end{verbatim}
-%
-In the command, \texttt{stat\_analyze} means we want to perform Hybrid AARA
-(instead of the conventional AARA).
-%
-The input \texttt{ticks} means the resource metric of our interest is the tick
-metric (instead of heap memory, for example).
-%
-The number 1 means we want to infer degree-1 polynomial cost bounds.
-%
-The input \texttt{append.ml} specifies the input file name, and the input
-\texttt{append} means we want to know a cost bound of the function
-\texttt{append} (instead of other functions in the same file).
-%
-Finally, the input \texttt{config\_opt.json} specifies the configuration file
-for Hybrid \Opt{}.
-
-In the output printed on the stdout, you should find
-\begin{verbatim}
-== append :
-
-[int list; int list] -> int list
-
-Non-zero annotations of the argument:
-    0.85  <--  ([::(*)], [])
-
-Non-zero annotations of result:
-
-Simplified bound:
-    0.85*M
-  where
-    M is the number of ::-nodes of the 1st component of the argument
-\end{verbatim}
-%
-It means that the cost bound inferred by Hybrid \Opt{} is $0.85 \cdot M$, where
-$M$ is the first input's length.
-
-\subsection{Hybrid \BayesWC{}}
-
-Next, to perform Hybrid \BayesWC{}, run
-\begin{verbatim}
-# main stat_analyze ticks 1 -m append.ml append -config config_bayeswc.json
-\end{verbatim}
-where the configuration file is now \texttt{config\_bayeswc.json}, which
-contains hyperparameters for Bayesian inference.
-%
-The analysis should finish in between 40 and 50 seconds.
-%
-Its output on the stdout should contain
-\begin{verbatim}
-== append :
-
-  [int list; int list] -> int list
-
-  Non-zero annotations of the argument:
-(avg, std) = (   2.18047,   0.633256)  <--
-                                         ([::(*)], [])
-(avg, std) = ( 0.0101388,  0.0158341)  <--  ([], [::(*)])
-(avg, std) = (         0,          0)  <--  ([], [])
-
-  Non-zero annotations of result:
-(avg, std) = (         0,          0)  <--
-                                   [::(*)]
-(avg, std) = (         0,          0)  <--  []
-
-  Simplified bound:
-     0.0101388*L + 2.18047*M
-   where
-     L is the number of ::-nodes of the 2nd component of the argument
-     M is the number of ::-nodes of the 1st component of the argument
-\end{verbatim}
-%
-Unlike Hybrid Opt{} that infers a single cost bound, Hybrid \BayesWC{} returns a
-collection of cost bounds, which approximate their posterior distribution.
-%
-In the stdout, 0.0101388 is the average degree-one coefficient for the first
-input in the posterior distribution, and likewise, 2.18047 is the average
-coefficient for the second input.
-
-\subsection{Hybrid \BayesPC{}}
-
-To perform Hybrid \BayesPC{}, run
-\begin{verbatim}
-# main stat_analyze ticks 1 -m append.ml append -config config_bayespc.json
-\end{verbatim}
-using the configuration file \texttt{config\_bayespc.json}.
-%
-The analysis should terminate within 90 seconds.
-%
-The output printed on the stdout should contain
-\begin{verbatim}
-== append :
-
-  [int list; int list] -> int list
-
-  Non-zero annotations of the argument:
-(avg, std) = (   2.03295,   0.228391)  <--  
-                                         ([::(*)], [])
-(avg, std) = (  0.281939,   0.146543)  <--  ([], [::(*)])
-(avg, std) = (  0.164309,  0.0824471)  <--  ([], [])
-
-  Non-zero annotations of result:
-(avg, std) = (         0,          0)  <--  
-                                   [::(*)]
-(avg, std) = (         0,          0)  <--  []
-
-  Simplified bound:
-     0.164309 + 0.281939*L + 2.03295*M
-   where
-     L is the number of ::-nodes of the 2nd component of the argument
-     M is the number of ::-nodes of the 1st component of the argument
-\end{verbatim}
-where \texttt{0.164309 + 0.281939*L + 2.03295*M} contains the average
-coefficients.
+\section{Step-by-Step Instructions}

### 2024-03-06 README/getting_started_guide.tex
Disabled LaTex for rendering plot labels

@@
 \end{verbatim}
+The current working directory is
+\texttt{/home/hybrid\_aara/benchmark\_suite/playground}.
 
-In the initial working directory, we have a file \texttt{append.ml} that stores
-the \texttt{append} function written in OCaml.
+In this directory, we have a file \texttt{append.ml} that stores an OCaml
+function \texttt{append}.
 %
@@
 
-Hybrid RaML's executable is the file \texttt{/home/hybrid\_aara/raml/main}, and
-its location has already been added to the \texttt{PATH} variable so that we can
+Hybrid RaML's executable is the file \texttt{/home/hybrid\_aara/raml/main}.
+%
+Its location has already been added to the \texttt{PATH} variable so that we can
 call Hybrid RaML by running \texttt{main} anywhere in the filesystem.
 %
-Hybrid AARA (and its artifact Hybrid RaML) provides three types of hybrid
+Hybrid AARA (and its implementation Hybrid RaML) provides three types of hybrid
 resource analysis: Hybrid \Opt{}, Hybrid \BayesWC{}, and Hybrid \BayesPC{}.
@@
 %
-In the command, \texttt{stat\_analyze} means we want to perform Hybrid AARA
+In the command line, \texttt{stat\_analyze} means we perform Hybrid AARA
 (instead of the conventional AARA).
 %
-The input \texttt{ticks} means the resource metric of our interest is the tick
-metric (instead of heap memory, for example).
+The argument \texttt{ticks} means the resource metric of our interest is the
+tick metric (instead of heap memory, for example).
 %
-The number 1 means we want to infer degree-1 polynomial cost bounds.
+The argument 1 means we want to infer degree-1 polynomial cost bounds.
 %
-The input \texttt{append.ml} specifies the input file name, and the input
-\texttt{append} means we want to know a cost bound of the function
-\texttt{append} (instead of other functions in the same file).
+The argument \texttt{append.ml} specifies the input file name, and the argument
+\texttt{append} specifies the function whose cost bound we want to infer.
 %
-Finally, the input \texttt{config\_opt.json} specifies the configuration file
-for Hybrid \Opt{}.
+Finally, the argument \texttt{config\_opt.json} is the configuration file for
+Hybrid \Opt{}.
 
@@
 %
-It means that the cost bound inferred by Hybrid \Opt{} is $0.85 \cdot M$, where
-$M$ is the first input's length.
+It means that the cost bound of the function \texttt{append} inferred by Hybrid
+\Opt{} is $0.85 \cdot M$, where $M$ is the first input's length.
 
@@
 %
-Its output on the stdout should contain
+Its output on the stdout should be close to
 \begin{verbatim}
@@
 %
-The output printed on the stdout should contain
+The output printed on the stdout should be close to
 \begin{verbatim}
@@
 \end{verbatim}
-where \texttt{0.164309 + 0.281939*L + 2.03295*M} contains the average
-coefficients.
+where each coefficient in the inference result \texttt{0.164309 + 0.281939*L +
+  2.03295*M} is the average coefficient.

### 2024-03-06 README/step_by_step_instructions.tex
Disabled LaTex for rendering plot labels

@@
 \section{Step-by-Step Instructions}
+
+\subsection{Benchmark Suite}
+
+The artifact contains 10 benchmark programs for Hybrid AARA.
+%
+As listed in Section 7 of the paper, these benchmarks are: \texttt{MapAppend},
+\texttt{Concat}, \texttt{InsertionSort2}, \texttt{QuickSort},
+\texttt{QuickSelect}, \texttt{MedianOfMedians}, \texttt{ZAlgorithm},
+\texttt{BubbleSort}, \texttt{Round}, and \texttt{EvenOddTail}.
+%
+Inside the artifact, these benchmarks are referred to as \texttt{append},
+\texttt{concat}, \texttt{insertion\_sort}, \texttt{quicksort},
+\texttt{quickselect}, \texttt{linear\_select}, \texttt{z\_algorithm},
+\texttt{bubble\_sort}, \texttt{round}, and \texttt{even\_split\_odd\_tail}.
+%
+We have tested both data-driven resource analysis and hybrid resource analysis
+on the first seven benchmarks, and only data-driven resource analysis on the
+remaining three benchmarks.
+
+Inside the benchmark directory \texttt{/home/hybrid\_aara/benchmark\_suite},
+each benchmark has its own directory.
+%
+Furthermore, inside the benchmarks' directories, we have the following
+directories:
+\begin{enumerate}
+  \item \texttt{utility}: Python source files that contain (i)
+        benchmark-specific configurations for hybrid resource analysis and (ii)
+        functions for analyzing the inference result.
+  \item \texttt{bin}: input and output files for Hybrid RaML.
+  \item \texttt{images}: plots of inferred cost bounds.
+\end{enumerate}
+
+For each benchmark, the directory \texttt{bin} already contains the experiment
+results that we reported in the paper.
+%
+We will demonstrate how to generate the experiment results from scratch in
+\cref{sec:generate experiment results}.
+
+\subsection{Display Experiment Results}
+
+We demonstrate how to create tables and plots in the paper from the experiment
+results that are stored in each benchmark's \texttt{bin} directories.
+
+\paragraph{Table~1}
+
+In Table~1 in the paper, the 4\textsuperscript{th} and 5\textsuperscript{th}
+columns display the proportions of sound cost bounds inferred by data-driven and
+hybrid resource analyses, respectively.
+%
+To display these two columns, run
+\begin{verbatim}
+# cd /home/hybrid_aara/benchmark_suite/toolbox
+# python3 run_analysis.py soundness
+\end{verbatim}
+
+The 6\textsuperscript{th} and 7\textsuperscript{th} columns of Table~1 display
+the analysis time of data-driven hybrid resource analyses, respectively.
+To display these two columns, run
+\begin{verbatim}
+# cd /home/hybrid_aara/benchmark_suite/toolbox
+# python3 run_analysis.py time
+\end{verbatim}
+
+\paragraph{Figure~5}
+
+Figure~5 in the paper displays relative errors of 5 selected benchmarks.
+%
+To create this plot, run
+\begin{verbatim}
+# cd /home/hybrid_aara/benchmark_suite/toolbox
+# python3 visualization_relative_errors.py
+\end{verbatim}
+%
+This command creates a plot and stores it as a file
+\texttt{relative\_errors.pdf} inside the directory
+\texttt{/home/hybrid\_aara/benchmark\_suite/images}.
+%
+To view the plot, we first transfer the plot from the Docker container to the
+local filesystem.
+%
+Run the following command in the terminal of your local machine:
+\begin{verbatim}
+$ docker cp hybrid_aara:/home/hybrid_aara/benchmark_suite/images/relative_errors.pdf 
+    <path_to_local_directory>
+\end{verbatim}
+where the second argument \texttt{<path\_to\_local\_directory>} is the
+destination directory on your local filesystem.
+%
+You can then view it on your local machine.
+
+\subsection{Generate Experiment Results}
+\label{sec:generate experiment results}

### 2024-03-06 benchmark_suite/toolbox/run_analysis.py

@@ -1,4 +1,5 @@
 import os
+import sys
 import numpy as np
 
 from benchmark_manipulation import get_module, get_list_benchmark_hybrid_mode
@@ -616,21 +617,22 @@ def display_execution_time(execution_time_all_benchmarks):
 
 
 if __name__ == "__main__":
-    # analyze_inference_result_all_benchmarks()
+    script_arg = sys.argv[1]
 
-    print("Proportions of sound cost bounds of benchmarks")
-    proportion_sound_cost_bounds_dict = calculate_desired_quantity_all_benchmarks(
-        get_proportion_sound_cost_bounds)
-    display_proportion_sound_cost_bounds(proportion_sound_cost_bounds_dict)
-    print()
-
-    print("Relative errors of benchmarks")
-    relative_error = calculate_desired_quantity_all_benchmarks(
-        analyze_relative_errors)
-    display_relative_errors_all_benchmarks(relative_error)
-    print()
-
-    print("Analysis time of Hybrid AARA")
-    execution_time_dict = calculate_desired_quantity_all_benchmarks(
-        get_execution_time)
-    display_execution_time(execution_time_dict)
+    if script_arg == "plot":
+        analyze_inference_result_all_benchmarks()
+    elif script_arg == "soundness":
+        print("Proportions of sound cost bounds of benchmarks")
+        proportion_sound_cost_bounds_dict = calculate_desired_quantity_all_benchmarks(
+            get_proportion_sound_cost_bounds)
+        display_proportion_sound_cost_bounds(proportion_sound_cost_bounds_dict)
+    elif script_arg == "relative_error":
+        print("Relative errors of benchmarks")
+        relative_error = calculate_desired_quantity_all_benchmarks(
+            analyze_relative_errors)
+        display_relative_errors_all_benchmarks(relative_error)
+    else:
+        print("Analysis time of Hybrid AARA")
+        execution_time_dict = calculate_desired_quantity_all_benchmarks(
+            get_execution_time)
+        display_execution_time(execution_time_dict)

### 2024-03-06 benchmark_suite/toolbox/run_experiment.py

@@ -1,7 +1,9 @@
 import multiprocessing
+import sys
 from joblib import Parallel, delayed
 
-from benchmark_manipulation import get_module, get_list_benchmark_hybrid_mode
+from benchmark_manipulation import get_module, get_list_benchmark_hybrid_mode, \
+    list_benchmarks_data_driven_hybrid
 from aara import run_aara
 
 
@@ -74,4 +76,18 @@ def run_all_benchmarks():
 
 
 if __name__ == "__main__":
-    run_all_benchmarks()
+
+    if sys.argv[1] == "all":
+        run_all_benchmarks()
+    else:
+        # The user provides both a benchmark name and hybrid mode
+        if len(sys.argv) == 3:
+            benchmark_name = sys.argv[1]
+            hybrid_mode = sys.argv[2]
+            run_experiment_benchmark_hybrid_mode(benchmark_name, hybrid_mode)
+        # The user only provides a benchmark name, but not a hybrid mode
+        else:
+            benchmark_name = sys.argv[1]
+            run_experiment_benchmark_hybrid_mode(benchmark_name, "data_driven")
+            if benchmark_name in list_benchmarks_data_driven_hybrid:
+                run_experiment_benchmark_hybrid_mode(benchmark_name, "hybrid")

### 2024-03-06 benchmark_suite/toolbox/visualization.py

@@ -8,13 +8,13 @@ FIGSIZE = (3.5, 3)
 # Originally, we also included the line \usepackage[varqu]{zi4} under
 # 'text.latex.preamble' in order to load the LaTex package zi4. However, it
 # causes an error in rendering some of the plots.
-plt.rcParams.update({
-    "font.family": "serif",
-    "text.usetex": True,
-    "text.latex.preamble": r"""
-        \usepackage[tt=false]{libertine}
-        \usepackage[libertine]{newtxmath}"""
-})
+# plt.rcParams.update({
+#     "font.family": "serif",
+#     "text.usetex": True,
+#     "text.latex.preamble": r"""
+#         \usepackage[tt=false]{libertine}
+#         \usepackage[libertine]{newtxmath}"""
+# })
 
 
 # Save a plot

### 2024-03-06 benchmark_suite/toolbox/visualization_relative_errors.py

@@ -1,18 +1,18 @@
 import os
 import matplotlib.gridspec as gridspec
-from run_experiment import calculate_desired_quantity_all_benchmarks, analyze_relative_errors
+from run_analysis import calculate_desired_quantity_all_benchmarks, analyze_relative_errors
 import matplotlib.pyplot as plt
 import itertools
 
 
-plt.rcParams.update({
-    "font.family": "serif",
-    "text.usetex": True,
-    'text.latex.preamble': r"""
-        \usepackage[tt=false]{libertine}
-        \usepackage[varqu]{zi4}
-        \usepackage[libertine]{newtxmath}"""
-})
+# plt.rcParams.update({
+#     "font.family": "serif",
+#     "text.usetex": True,
+#     'text.latex.preamble': r"""
+#         \usepackage[tt=false]{libertine}
+#         \usepackage[varqu]{zi4}
+#         \usepackage[libertine]{newtxmath}"""
+# })
 
 c = ['tab:red', 'tab:blue', 'y']
 m = 'o'

### 2024-03-07 benchmark_suite/Concat/utility/annotated_code_cost.py
Changed the benchmark names to be consistent with the paper

@@ -1,7 +1,7 @@
 import os
 import sys
 module_path = os.path.expanduser(os.path.join(
-    "/home", "hybrid_aara", "benchmark_suite", "concat", "utility"))
+    "/home", "hybrid_aara", "benchmark_suite", "Concat", "utility"))
 if module_path not in sys.path:
     sys.path.append(module_path)
 

### 2024-03-07 benchmark_suite/InsertionSort2/utility/annotated_code_cost.py

@@ -1,7 +1,7 @@
 import os
 import sys
 module_path = os.path.expanduser(os.path.join(
-    "/home", "hybrid_aara", "benchmark_suite", "insertion_sort", "utility"))
+    "/home", "hybrid_aara", "benchmark_suite", "InsertionSort2", "utility"))
 if module_path not in sys.path:
     sys.path.append(module_path)
 

### 2024-03-07 benchmark_suite/MapAppend/utility/cost_evaluation.py

@@ -1,6 +1,3 @@
-import numpy as np
-import csv
-
 # Cost of running append
 
 

### 2024-03-07 benchmark_suite/MedianOfMedians/utility/annotated_code_cost.py

@@ -1,7 +1,7 @@
 import os
 import sys
 module_path = os.path.expanduser(os.path.join(
-    "/home", "hybrid_aara", "benchmark_suite", "linear_select", "utility"))
+    "/home", "hybrid_aara", "benchmark_suite", "MedianOfMedians", "utility"))
 if module_path not in sys.path:
     sys.path.append(module_path)
 

### 2024-03-07 benchmark_suite/QuickSelect/utility/annotated_code_cost.py

@@ -1,36 +1,48 @@
 import os
 import sys
 module_path = os.path.expanduser(os.path.join(
-    "/home", "hybrid_aara", "benchmark_suite", "quicksort", "utility"))
+    "/home", "hybrid_aara", "benchmark_suite", "QuickSelect", "utility"))
 if module_path not in sys.path:
     sys.path.append(module_path)
 
 from cost_evaluation import partition, partition_cost
 
 
-def quicksort_all_partition_calls(input_list):
+def quickselect_all_partition_calls(integer_list_pair):
+    index, input_list = integer_list_pair
     if len(input_list) == 0:
-        return []
+        raise Exception("The input list is empty")
+    elif len(input_list) == 1:
+        if index == 0:
+            return []
+        else:
+            raise Exception("The index should be zero for a singleton list")
     else:
         head_element = input_list[0]
         lower_list, upper_list = partition(head_element, input_list[1:])
-        list_partition_calls_lower_list = quicksort_all_partition_calls(
-            lower_list)
-        list_partition_calls_upper_list = quicksort_all_partition_calls(
-            upper_list)
-        return [(head_element, input_list[1:], lower_list, upper_list)] + list_partition_calls_lower_list + list_partition_calls_upper_list
+        if index < len(lower_list):
+            cumulative_partition_calls = quickselect_all_partition_calls(
+                (index, lower_list))
+            return [(head_element, input_list[1:], lower_list, upper_list)] + cumulative_partition_calls
+        elif index == len(lower_list):
+            return [(head_element, input_list[1:], lower_list, upper_list)]
+        else:
+            cumulative_partition_calls = quickselect_all_partition_calls(
+                (index - len(lower_list) - 1, upper_list))
+            return [(head_element, input_list[1:], lower_list, upper_list)] + cumulative_partition_calls
 
 
 def get_all_partition_calls(input_data):
     input_data_partition = []
-    for input_list in input_data:
-        input_data_partition += quicksort_all_partition_calls(input_list)
+    for integer_list_pair in input_data:
+        input_data_partition += quickselect_all_partition_calls(
+            integer_list_pair)
     return input_data_partition
 
 
-def evaluate_cost_partition(partition_call, modulo=5, lower_cost=0.5):
+def evaluate_cost_partition(partition_call):
     pivot, input_list, _, _ = partition_call
[…]

### 2024-03-07 benchmark_suite/QuickSort/utility/annotated_code_cost.py

@@ -1,48 +1,36 @@
 import os
 import sys
 module_path = os.path.expanduser(os.path.join(
-    "/home", "hybrid_aara", "benchmark_suite", "quickselect", "utility"))
+    "/home", "hybrid_aara", "benchmark_suite", "QuickSort", "utility"))
 if module_path not in sys.path:
     sys.path.append(module_path)
 
 from cost_evaluation import partition, partition_cost
 
 
-def quickselect_all_partition_calls(integer_list_pair):
-    index, input_list = integer_list_pair
+def quicksort_all_partition_calls(input_list):
     if len(input_list) == 0:
-        raise Exception("The input list is empty")
-    elif len(input_list) == 1:
-        if index == 0:
-            return []
-        else:
-            raise Exception("The index should be zero for a singleton list")
+        return []
     else:
         head_element = input_list[0]
         lower_list, upper_list = partition(head_element, input_list[1:])
-        if index < len(lower_list):
-            cumulative_partition_calls = quickselect_all_partition_calls(
-                (index, lower_list))
-            return [(head_element, input_list[1:], lower_list, upper_list)] + cumulative_partition_calls
-        elif index == len(lower_list):
-            return [(head_element, input_list[1:], lower_list, upper_list)]
-        else:
-            cumulative_partition_calls = quickselect_all_partition_calls(
-                (index - len(lower_list) - 1, upper_list))
-            return [(head_element, input_list[1:], lower_list, upper_list)] + cumulative_partition_calls
+        list_partition_calls_lower_list = quicksort_all_partition_calls(
+            lower_list)
+        list_partition_calls_upper_list = quicksort_all_partition_calls(
+            upper_list)
+        return [(head_element, input_list[1:], lower_list, upper_list)] + list_partition_calls_lower_list + list_partition_calls_upper_list
 
 
 def get_all_partition_calls(input_data):
     input_data_partition = []
-    for integer_list_pair in input_data:
-        input_data_partition += quickselect_all_partition_calls(
-            integer_list_pair)
+    for input_list in input_data:
+        input_data_partition += quicksort_all_partition_calls(input_list)
     return input_data_partition
 
 
-def evaluate_cost_partition(partition_call):
+def evaluate_cost_partition(partition_call, modulo=5, lower_cost=0.5):
     pivot, input_list, _, _ = partition_call
-    return partition_cost(pivot, input_list)
[…]

### 2024-03-07 benchmark_suite/ZAlgorithm/utility/annotated_code_cost.py

@@ -1,7 +1,7 @@
 import os
 import sys
 module_path = os.path.expanduser(os.path.join(
-    "/home", "hybrid_aara", "benchmark_suite", "z_algorithm", "utility"))
+    "/home", "hybrid_aara", "benchmark_suite", "ZAlgorithm", "utility"))
 if module_path not in sys.path:
     sys.path.append(module_path)
 

### 2024-03-07 benchmark_suite/ZAlgorithm/utility/ocaml_code.py

@@ -7,7 +7,8 @@ if module_path not in sys.path:
 from input_data_generation import convert_lists_python_to_ocaml
 
 
-# Create OCaml code
+# Create OCaml code. Z-algorithm is described here:
+# https://cp-algorithms.com/string/z-function.html.
 
 
 z_algorithm_data_driven_ocaml_code = \

### 2024-03-07 benchmark_suite/toolbox/benchmark_manipulation.py

@@ -28,10 +28,10 @@ def get_module(module_name, analysis_info):
 
 
 list_benchmarks_data_driven_hybrid = [
-    "append", "concat", "insertion_sort", "linear_select", "quickselect", "quicksort", "z_algorithm"]
+    "MapAppend", "Concat", "InsertionSort2", "MedianOfMedians", "QuickSelect", "QuickSort", "ZAlgorithm"]
 
 list_benchmarks_data_driven = [
-    "bubble_sort", "round", "even_split_odd_tail"]
+    "BubbleSort", "Round", "EvenSplitOddTail"]
 
 
 def get_list_benchmark_hybrid_mode():

### 2024-03-07 benchmark_suite/toolbox/generate_sigma.py

@@ -3,7 +3,8 @@ import matplotlib.pyplot as plt
 import os
 import json
 
-from benchmark_manipulation import get_module
+from benchmark_manipulation import get_module, list_benchmarks_data_driven_hybrid, \
+    list_benchmarks_data_driven
 from pathnames import bin_directory
 from json_manipulation import read_input_data_json
 
@@ -24,12 +25,8 @@ def compute_line(start_point, end_point, xs):
 # List all benchmarks and hybrid modes
 
 
-benchmark_names_data_driven_and_hybrid = [
-    "append", "concat", "insertion_sort", "quicksort", "quickselect", "linear_select", "z_algorithm"]
-benchmark_names_data_driven = ["bubble_sort", "round", "even_split_odd_tail"]
-
 list_analysis_info = []
-for benchmark_name in benchmark_names_data_driven_and_hybrid:
+for benchmark_name in list_benchmarks_data_driven_hybrid:
     analysis_info_data_driven = {"benchmark_name": benchmark_name,
                                  "hybrid_mode": "data_driven"}
     analysis_info_hybrid = {"benchmark_name": benchmark_name,
@@ -37,7 +34,7 @@ for benchmark_name in benchmark_names_data_driven_and_hybrid:
     list_analysis_info.append(analysis_info_data_driven)
     list_analysis_info.append(analysis_info_hybrid)
 
-for benchmark_name in benchmark_names_data_driven:
+for benchmark_name in list_benchmarks_data_driven:
     analysis_info_data_driven = {"benchmark_name": benchmark_name,
                                  "hybrid_mode": "data_driven"}
     list_analysis_info.append(analysis_info_data_driven)
@@ -83,16 +80,16 @@ def get_input_coeff(analysis_info):
 
 
 num_highest_degree_coeffs_dict = {
-    "append": 2,
-    "bubble_sort": 1,
-    "concat": 3,
-    "even_split_odd_tail": 1,
-    "insertion_sort": 1,
-    "quickselect": 1,
-    "linear_select": 1,
-    "z_algorithm": 1,
-    "round": 1,
-    "quicksort": 1}
+    "MapAppend": 2,
+    "BubbleSort": 1,
+    "Concat": 3,
+    "EvenSplitOddTail": 1,
+    "InsertionSort2": 1,
+    "QuickSelect": 1,
+    "MedinaOfMedians": 1,
+    "ZAlgorithm": 1,
+    "Round": 1,
+    "QuickSort": 1}
 
 
 def get_coeff_statistic(analysis_info):

### 2024-03-07 benchmark_suite/toolbox/run_analysis.py

@@ -9,6 +9,7 @@ from visualization import plot_cost_gaps_opt, plot_cost_gaps_bayesian, \
     plot_gaps_ground_truth_opt, plot_gaps_ground_truth_bayesian, \
     plot_inferred_cost_bound, plot_inferred_cost_bound_3D, \
     plot_posterior_distribution_cost_bound, plot_median_cost_bound_3D
+from visualization_relative_errors import plot_relative_errors_selected_benchmarks
 from relative_errors import calculate_relative_error_opt_representative_samples, \
     calculate_relative_error_bayesian_representative_samples, \
     calculate_relative_error_opt_representative_samples_2D, \
@@ -160,16 +161,16 @@ def analyze_inference_result_cost_gaps_ground_truth(analysis_info, plot_name, sa
 
 
 cost_bound_plot_lim_dict = {
-    "append": 70,
-    "bubble_sort": 8000,
-    "concat": 3000,
-    "even_split_odd_tail": 400,
-    "insertion_sort": 400,
-    "linear_select": 1500,
-    "quickselect": 2000,
-    "quicksort": 50000,
-    "round": 400,
-    "z_algorithm": 300
+    "MapAppend": 70,
+    "BubbleSort": 8000,
+    "Concat": 3000,
+    "EvenSplitOddTail": 400,
+    "InsertionSort2": 400,
+    "MedianOfMedians": 1500,
+    "QuickSelect": 2000,
+    "QuickSort": 50000,
+    "Round": 400,
+    "ZAlgorithm": 300
 }
 
 
@@ -209,7 +210,7 @@ def analyze_inference_result_cost_bound(analysis_info, plot_name, save, show, ax
     get_predicted_cost = cost_evaluation_module.get_predicted_cost
     lim = cost_bound_plot_lim_dict[benchmark_name]
 
-    if benchmark_name == "append" or benchmark_name == "concat":
+    if benchmark_name == "MapAppend" or benchmark_name == "Concat":
         if data_analysis_mode == "opt":
             plot_function = plot_inferred_cost_bound_3D
         else:
@@ -311,12 +312,12 @@ def analyze_relative_errors(analysis_info):
         decompose_inference_result = read_inference_result_module.decompose_posterior_distribution
     get_relative_gap_ground_truth = cost_evaluation_module.get_relative_gap_ground_truth
 
-    if benchmark_name == "append":
+    if benchmark_name == "MapAppend":
         if data_analysis_mode == "opt":
[…]

### 2024-03-07 benchmark_suite/toolbox/run_experiment.py

@@ -27,7 +27,7 @@ def run_single_experiment(analysis_info):
     degree = config_module.degree
 
     # Get input data
-    if (benchmark_name == "quickselect" or benchmark_name == "quicksort") and hybrid_mode == "hybrid" and data_analysis_mode == "bayespc":
+    if (benchmark_name == "QuickSelect" or benchmark_name == "QuickSort") and hybrid_mode == "hybrid" and data_analysis_mode == "bayespc":
         input_data = config_module.input_data_extracted
     else:
         input_data = config_module.input_data

### 2024-03-07 benchmark_suite/toolbox/visualization.py

@@ -355,7 +355,7 @@ def plot_inferred_cost_bound(runtime_cost_data, inferred_coefficients,
 
     # Use a log scale for the y axis in quicksort
     benchmark_name = analysis_info["benchmark_name"]
-    if benchmark_name == "quicksort":
+    if benchmark_name == "QuickSort":
         ax.set_ylim(1, ylim)
         ax.set_yscale('log')
 
@@ -371,7 +371,7 @@ def plot_inferred_cost_bound(runtime_cost_data, inferred_coefficients,
 
     # Legend
     if axis_label:
-        if benchmark_name == "quicksort":
+        if benchmark_name == "QuickSort":
             ax.legend(loc='lower right', framealpha=1, fancybox=False)
         else:
             ax.legend(loc='upper left', framealpha=1, fancybox=False)
@@ -443,7 +443,7 @@ def plot_posterior_distribution_cost_bound(runtime_cost_data, posterior_distribu
 
     # Use a log scale for the y axis in quicksort
     benchmark_name = analysis_info["benchmark_name"]
-    if benchmark_name == "quicksort":
+    if benchmark_name == "QuickSort":
         ax.set_ylim(1, ylim)
         ax.set_yscale('log')
 
@@ -458,7 +458,7 @@ def plot_posterior_distribution_cost_bound(runtime_cost_data, posterior_distribu
         ax.set_yticks([], minor=True)
 
     # Legend
-    # if benchmark_name == "quicksort":
+    # if benchmark_name == "QuickSort":
     #     ax.legend(loc='lower right', framealpha=1, fancybox=False)
     # else:
     #     ax.legend(loc='upper left', framealpha=1, fancybox=False)

### 2024-03-07 benchmark_suite/toolbox/visualization_relative_errors.py

@@ -1,6 +1,5 @@
 import os
 import matplotlib.gridspec as gridspec
-from run_analysis import calculate_desired_quantity_all_benchmarks, analyze_relative_errors
 import matplotlib.pyplot as plt
 import itertools
 
@@ -68,7 +67,7 @@ def plot_relative_errors_benchmark(ax, relative_error_benchmark):
     ax.set_ylim([ymin, None])
 
 
-def plot_relative_errors_selected_benchmarks():
+def plot_relative_errors_selected_benchmarks(relative_error):
     gs_kw = dict(width_ratios=[2, 2, 2, 1, 1])
     fig, axes = plt.subplots(
         tight_layout=True, gridspec_kw=gs_kw, figsize=(10, 3), ncols=5)
@@ -82,15 +81,12 @@ def plot_relative_errors_selected_benchmarks():
     #     fig.add_subplot(gs[1, :]),
     # ]
 
-    relative_error = calculate_desired_quantity_all_benchmarks(
-        analyze_relative_errors)
-
-    plot_relative_errors_benchmark(axes[0], relative_error['quicksort'])
-    plot_relative_errors_benchmark(axes[1], relative_error['quickselect'])
-    plot_relative_errors_benchmark(axes[2], relative_error['linear_select'])
-    plot_relative_errors_benchmark(axes[3], relative_error['round'])
+    plot_relative_errors_benchmark(axes[0], relative_error['QuickSort'])
+    plot_relative_errors_benchmark(axes[1], relative_error['QuickSelect'])
+    plot_relative_errors_benchmark(axes[2], relative_error['MedianOfMedians'])
+    plot_relative_errors_benchmark(axes[3], relative_error['Round'])
     plot_relative_errors_benchmark(
-        axes[4], relative_error['even_split_odd_tail'])
+        axes[4], relative_error['EvenSplitOddTail'])
 
     axes[0].set_title(r'\texttt{QuickSort}')
     axes[1].set_title(r'\texttt{QuickSelect}')
@@ -144,7 +140,3 @@ def plot_relative_errors_selected_benchmarks():
         os.makedirs(image_directory_path)
     image_path = os.path.join(image_directory_path, "relative_errors.pdf")
     plt.savefig(image_path, format="pdf", dpi=300, bbox_inches='tight')
-
-
-if __name__ == "__main__":
-    plot_relative_errors_selected_benchmarks()

### 2024-03-07 README/step_by_step_instructions.tex
Fleshed out the explanation of how to produce plots and tables

@@
 %
-Inside the artifact, these benchmarks are referred to as \texttt{append},
-\texttt{concat}, \texttt{insertion\_sort}, \texttt{quicksort},
-\texttt{quickselect}, \texttt{linear\_select}, \texttt{z\_algorithm},
-\texttt{bubble\_sort}, \texttt{round}, and \texttt{even\_split\_odd\_tail}.
+Inside the artifact, the benchmark \texttt{EvenOddTail} goes by its full name,
+\texttt{EvenSplitOddTail}, instead of its shorthand \texttt{EvenOddTail} used
+throughout the paper.
 %
@@
 
-For each benchmark, the directory \texttt{bin} already contains the experiment
-results that we reported in the paper.
-%
-We will demonstrate how to generate the experiment results from scratch in
-\cref{sec:generate experiment results}.
-
 \subsection{Display Experiment Results}
 
-We demonstrate how to create tables and plots in the paper from the experiment
-results that are stored in each benchmark's \texttt{bin} directories.
+In this section, we demonstrate how to create tables and plots in the paper from
+the experiment results that are stored in each benchmark's \texttt{bin}
+directories.
+%
+In the Docker container, the directory \texttt{bin} of each benchmark already
+contains the experiment results that we reported in the paper.
+%
+We will later demonstrate how to generate the experiment results from scratch in
+\cref{sec:generate experiment results}.
 
@@
 In Table~1 in the paper, the 4\textsuperscript{th} and 5\textsuperscript{th}
-columns display the proportions of sound cost bounds inferred by data-driven and
+columns display the percentages of sound cost bounds inferred by data-driven and
 hybrid resource analyses, respectively.
@@
 # cd /home/hybrid_aara/benchmark_suite/toolbox
-# python3 visualization_relative_errors.py
+# python3 run_analysis.py plot_relative_errors
 \end{verbatim}
@@
 %
-To view the plot, we first transfer the plot from the Docker container to the
-local filesystem.
+To view the plot, we first transfer it from the Docker container to your local
+filesystem.
 %
@@
 \begin{verbatim}
-$ docker cp hybrid_aara:/home/hybrid_aara/benchmark_suite/images/relative_errors.pdf 
-    <path_to_local_directory>
+$ docker cp hybrid_aara:/home/hybrid_aara/benchmark_suite\
+/images/relative_errors.pdf \
+<path-to-local-directory>
 \end{verbatim}
-where the second argument \texttt{<path\_to\_local\_directory>} is the
+where the second argument \texttt{<path-to-local-directory>} is a desired
 destination directory on your local filesystem.
 %
-You can then view it on your local machine.
+You can then view the plot on your local machine.
+
+\paragraph{Figures~6--24}
+
+For Figures~6--24 in the paper, to create them, run
+\begin{verbatim}
+# cd /home/hybrid_aara/benchmark_suite/toolbox
+# python3 run_analysis.py plot
+\end{verbatim}
+%
+This command creates all plots of inference results and stores them in the
+directory \texttt{benchmark\_suite/<benchmark-name>/images}.
+%
+For example, for hybrid BayesWC performed on \texttt{QuickSort}, we can
+find its plot in the file \texttt{inferred\_cost\_bound.pdf} in the directory
+\texttt{benchmark\_suite/QuickSort/images/hybrid/bayeswc}.
+
+To view the plot, again, we transfer it from the Docker container to your local
+filesystem.
+%
+Run this command on the terminal of the local machine:
+\begin{verbatim}
+$ docker cp hybrid_aara:/home/hybrid_aara/benchmark_suite\
+/QuickSort/images/hybrid/bayeswc/inferred_cost_bound.pdf \
+<path-to-local-directory>
+\end{verbatim}
+%
+You can then view the plot on your local machine.
+
+\paragraph{Tables~2--11}
+
+For Tables~2--11 in the paper, to create and display them on the stdout, run
+\begin{verbatim}
+# cd /home/hybrid_aara/benchmark_suite/toolbox
+# python3 run_analysis.py relative_errors
+\end{verbatim}
 
@@
 \label{sec:generate experiment results}
+
+\subsection{Source Code}

### 2024-03-07 README/getting_started_guide.tex
Fleshed out the explanation of how to produce plots and tables
Revised README

@@
 
-The artifact is wrapped inside the provided Docker image.
+The artifact is wrapped inside the accompanying Docker image
+\texttt{hybrid\_aara.tar.gz}.
 %
-To run it, first install Docker according to the instructions at
+Before running it, first install Docker as instructed here:
 \url{https://docs.docker.com/engine/install/}.
@@
 $ docker load --input hybrid_aara.tar.gz
-$ docker run -it --rm hybrid_aara
+$ docker run --name hybrid_aara -it --rm hybrid_aara
 root@fca41f6f696d:/home/hybrid_aara/benchmark_suite/playground#
 \end{verbatim}
-The current working directory is
-\texttt{/home/hybrid\_aara/benchmark\_suite/playground}.
+%
+Throughout this document, any command line starting with \texttt{\#} is executed
+inside the Docker container, and any command line starting with \texttt{\$} is
+executed in your local machine's terminal.
 
-In this directory, we have a file \texttt{append.ml} that stores an OCaml
-function \texttt{append}.
+The initial working directory \texttt{playground} has a file \texttt{append.ml},
+which stores an OCaml function \texttt{append}.
 %
@@
 Its location has already been added to the \texttt{PATH} variable so that we can
-call Hybrid RaML by running \texttt{main} anywhere in the filesystem.
+call Hybrid RaML by running \texttt{main} anywhere in the Docker container's
+filesystem.
 %
-Hybrid AARA (and its implementation Hybrid RaML) provides three types of hybrid
+Hybrid AARA (and its implementation Hybrid RaML) provides three modes of hybrid
 resource analysis: Hybrid \Opt{}, Hybrid \BayesWC{}, and Hybrid \BayesPC{}.
@@
 %
-The analysis should finish in between 40 and 50 seconds.
+The analysis should finish in 50 seconds.
 %
@@
 Unlike Hybrid Opt{} that infers a single cost bound, Hybrid \BayesWC{} returns a
-collection of cost bounds, which approximate their posterior distribution.
+collection of cost bounds, which approximate their posterior distribution in
+Bayesian inference.
 %
 In the stdout, 0.0101388 is the average degree-one coefficient for the first
-input in the posterior distribution, and likewise, 2.18047 is the average
+input in the posterior distribution, and 2.18047 is the average
 coefficient for the second input.
@@
 where each coefficient in the inference result \texttt{0.164309 + 0.281939*L +
-  2.03295*M} is the average coefficient.
+  2.03295*M} is the average of its posterior distribution.

### 2024-03-07 README/step_by_step_instructions.tex
Revised README

--- 2024-03-06 README/step_by_step_instructions.tex
@@
 \section{Step-by-Step Instructions}
+
+\subsection{Benchmark Suite}
+
+The artifact contains 10 benchmark programs for Hybrid AARA as listed in
+Section~7 of the paper.
+%
+These benchmarks are: \texttt{MapAppend}, \texttt{Concat},
+\texttt{InsertionSort2}, \texttt{QuickSort}, \texttt{QuickSelect},
+\texttt{MedianOfMedians}, \texttt{ZAlgorithm}, \texttt{BubbleSort},
+\texttt{Round}, and \texttt{EvenOddTail}.
+%
+Inside the artifact, the benchmark \texttt{EvenOddTail} goes by its full name,
+\texttt{EvenSplitOddTail}, instead of its shorthand \texttt{EvenOddTail} used
+in the paper.
+%
+The paper evaluates both purely data-driven resource analysis and hybrid
+resource analysis on the first seven benchmarks, and only data-driven resource
+analysis on the remaining three benchmarks.
+
+Inside the benchmark directory \texttt{/home/hybrid\_aara/benchmark\_suite},
+each benchmark has its own directory, which contains the following three
+subdirectories:
+\begin{enumerate}
+  \item \texttt{utility}: Python source files that contain (i)
+        benchmark-specific configurations for Hybrid AARA and (ii) functions for
+        analyzing the inference results.
+  \item \texttt{bin}: input and output files for Hybrid RaML.
+  \item \texttt{images}: plots of inferred cost bounds.
+\end{enumerate}
+
+\subsection{Display Experiment Results}
+\label{sec:display experiment results}
+
+In this section, we demonstrate how to produce tables and plots in the paper
+from the experiment results that are stored in each benchmark's \texttt{bin}
+directory.
+%
+In the Docker container, the \texttt{bin} directory of each benchmark already
+contains the experiment results that we reported in the paper.
+%
+We will demonstrate how to generate the experiment results from scratch in
+\cref{sec:generate experiment results}.
+
+The tables and plots produced by the artifact are different from the ones in the
+submitted version of the paper.
+%
+This is because, since the submission, we have adjusted the hyperparameters for
+\BayesWC{} and \BayesPC{} in order to an automatic procedure for choosing
+hyperparameters.
+%
+The updated experiments results still preserve our key claims in Section~7 of
+the paper.
+%
+The updated version of the paper accompanies the artifact.
+
+Go to the directory \texttt{/home/hybrid\_aara/benchmark\_suite/toolbox}.
+%
+Then run
+\begin{verbatim}
+# python3 run_analysis.py <table-or-plot-type>
+\end{verbatim}
+where \texttt{<table-or-plot-type>} specifies the type of tables or plots to
+produce.
+
+\paragraph{Soundness proportions}
+
+In Table~1 in the paper, the 4\textsuperscript{th} and 5\textsuperscript{th}
+columns display the percentages of sound cost bounds inferred by data-driven and
+hybrid resource analyses, respectively.
+%
+To display these two columns, run
+\begin{verbatim}
+# python3 run_analysis.py soundness
+\end{verbatim}
+
+This table supports the two key claims in our paper (Section~7).
+%
+Firstly, \BayesWC{} and \BayesPC{} have higher percentages of sound cost bounds
+than \Opt{} (in both data-driven and hybrid resource analysis).
+%
+Secondly, hybrid resource analysis (Hybrid \BayesWC{} and Hybrid \BayesPC{}) has
+higher percentages of sound cost bounds than purely data-driven resource
+analysis (Data-Driven \BayesWC{} and Data-Driven \BayesPC{}).
+
+\paragraph{Analysis time}
+
+The 6\textsuperscript{th} and 7\textsuperscript{th} columns of Table~1 display
+the analysis time of data-driven hybrid resource analyses, respectively.
+To display these two columns, run
+\begin{verbatim}
+# python3 run_analysis.py time
+\end{verbatim}
+
+\paragraph{Relative errors}
+
+Figure~5 in the paper displays relative errors of 5 selected benchmarks.
+%
+To produce this plot, run
+\begin{verbatim}
+# python3 run_analysis.py plot_relative_errors
+\end{verbatim}
+%
+This command produces a plot and stores it as
+\texttt{relative\_errors.pdf} inside the directory
+\texttt{/home/hybrid\_aara/benchmark\_suite/images}.
+%
+To view the plot, we first transfer it from the Docker container to your local
+filesystem.
+%
+Run the following command in your local machine's terminal:
+\begin{verbatim}
+$ docker cp hybrid_aara:/home/hybrid_aara/benchmark_suite\
+/images/relative_errors.pdf \
+<path-to-local-directory>
+\end{verbatim}
+where the second argument \texttt{<path-to-local-directory>} is a desired
+destination directory on your local filesystem.
+%
+You can then view the plot on your local machine.
+
+For Tables~2--11 in the paper, to create and display them on the stdout, run
+\begin{verbatim}
+# python3 run_analysis.py relative_errors
+\end{verbatim}
+
+\paragraph{Plots of inferred cost bounds}
+
+To produce Figures~6--24 in the paper, run
+\begin{verbatim}
+# python3 run_analysis.py plot
+\end{verbatim}
+%
+This command creates all plots of inference results and stores them in the
+directory \texttt{benchmark\_suite/<benchmark-name>/images}.
+%
+It should terminate in 4 minutes.
+
+For example, for Hybrid \BayesWC{} performed on the benchmark
+\texttt{QuickSort}, its plot is the file \texttt{inferred\_cost\_bound.pdf} in
+the directory
+\begin{verbatim}
+benchmark_suite/QuickSort/images/hybrid/bayeswc
+\end{verbatim}
+%
+To view the plot, we transfer it from the Docker container to your local
+filesystem.
+%
+Run this command in the local machine's terminal:
+\begin{verbatim}
+$ docker cp hybrid_aara:/home/hybrid_aara/benchmark_suite\
+/QuickSort/images/hybrid/bayeswc/inferred_cost_bound.pdf \
+<path-to-local-directory>
+\end{verbatim}
+%
+You can then view the plot on your local machine.
+
+\subsection{Generate Experiment Results}
+\label{sec:generate experiment results}
+
+This section demonstrates how to perform Hybrid AARA on the 10 benchmark
+programs.
+%
+First go to the directory \texttt{/home/hybrid\_aara/benchmark\_suite/toolbox}.
+%
+Then run
+\begin{verbatim}
+# python3 run_experiment.py <options>
+\end{verbatim}
+where \texttt{<options>} specifies the benchmark name and possibly also the
+analysis mode.
+%
+The inference result will be stored inside each benchmarks' \texttt{bin}
+directory.
+
+To perform Hybrid AARA on the benchmark \texttt{QuickSort} using purely
+data-driven resource analysis, run
+\begin{verbatim}
+# python3 run_experiment.py QuickSort data_driven
+\end{verbatim}
+%
+It will run Data-Driven \Opt{}, Data-Driven \BayesWC{}, and Data-Driven
+\BayesPC{}.
+%
+The analysis should finish within 2 minutes.
+%
+If we instead want to perform hybrid resource analysis,
+\begin{verbatim}
+# python3 run_experiment.py QuickSort hybrid
+\end{verbatim}
+%
+It will run Hybrid \Opt{}, Hybrid \BayesWC{}, and Hybrid \BayesPC{}.
+%
+The analysis should finish in 11 minutes.
+%
+To run both purely data-driven and hybrid resource analyses on the benchmark
+\texttt{QuickSort}, run
+\begin{verbatim}
+# python3 run_experiment.py QuickSort
+\end{verbatim}
+without specifying the analysis mode.
+
+Finally, to run all 10 benchmarks (under both purely data-driven and hybrid
+analyses), run
+\begin{verbatim}
+# python3 run_experiment.py all
+\end{verbatim}
+This can take up to 2 hours to run\footnote{We have tried Python's
+multiprocessing to run multiple benchmarks in parallel, but it did not work
+properly in Docker. So our artifact can only run benchmarks sequentially.}.
+
+To view the updated tables and plots of the new experiment results, follow the
+steps in \cref{sec:display experiment results}.
+%
+The experiment results for (Data-Driven and Hybrid) \BayesWC{} and \BayesPC{}
+after rerunning the experiments may look different from the tables and plots
+reported in the updated version of the paper.
+%
+This is because \BayesWC{} and \BayesPC{} run sampling-based Bayesian inference
+algorithms that are stochastic.
+%
+Nonetheless, there should not be any significant deviation.
+
+\subsection{Source Code}
+
+Our artifact contains three tools that we have built by ourselves: (i) Hybrid
+RaML (in OCaml), (ii) the volesti-RaML interface (in C++), and (iii) the
+benchmark suite (in Python).
+%
+Their source code is stored in directories \texttt{raml},
+\texttt{volesti\_raml\_interface}, and \texttt{benchmark\_suite} inside the
+project directory \texttt{/home/hybrid\_aara} in the Docker image.
+
+The project directory inside the image contains two additional directories.
+%
+The third-party C++ library volesti\footnote{Available here:
+\url{https://github.com/GeomScale/volesti}.} is stored in the directory
+\texttt{volesti}.
+%
+The linear-program solver COIN-OR CLP\footnote{Available here:
+\url{https://github.com/coin-or/Clp}.} is stored in the directory \texttt{clp}.
+
+The code for building a Docker image is publicly available on GitHub:
+\url{https://github.com/LongPham7/hybrid_aara_artifact}.
+%
+To build a Docker image, clone the GitHub repository and then run (in the root
+directory)
+\begin{verbatim}
+$ docker build -t hybrid_aara .
+\end{verbatim}
+%
+It will take 20--30 minutes.
+%
+The resulting image is named \texttt{hybrid\_aara} and is stored locally on your
+machine.
+%
+To run this image after it is built, run
+\begin{verbatim}
+$ docker run --name hybrid_aara -it --rm hybrid_aara
+\end{verbatim}
+%
+If you want to save the image as a tar archive and compress it, run
+\begin{verbatim}
+$ docker save hybrid_aara | gzip > hybrid_aara.tar.gz
+\end{verbatim}

### 2024-03-08 benchmark_suite/toolbox/benchmark_manipulation.py
Improved the pretty printing of tables

@@ -28,14 +28,14 @@ def get_module(module_name, analysis_info):
 
 
 list_benchmarks_data_driven_hybrid = [
-    "MapAppend", "Concat", "InsertionSort2", "MedianOfMedians", "QuickSelect", "QuickSort", "ZAlgorithm"]
+    "MapAppend", "Concat", "InsertionSort2", "MedianOfMedians",
+    "QuickSelect", "QuickSort", "ZAlgorithm"]
 
 list_benchmarks_data_driven = [
     "BubbleSort", "Round", "EvenSplitOddTail"]
 
 
 def get_list_benchmark_hybrid_mode():
-
     list_benchmark_hybrid_mode = []
     for benchmark_name in list_benchmarks_data_driven_hybrid:
         list_benchmark_hybrid_mode.append((benchmark_name, "data_driven"))

### 2024-03-08 benchmark_suite/toolbox/run_analysis.py

@@ -2,7 +2,8 @@ import os
 import sys
 import numpy as np
 
-from benchmark_manipulation import get_module, get_list_benchmark_hybrid_mode
+from benchmark_manipulation import get_module, get_list_benchmark_hybrid_mode, \
+    list_benchmarks_data_driven_hybrid, list_benchmarks_data_driven
 from pathnames import bin_directory
 from json_manipulation import read_input_data_json, read_execution_time_json
 from visualization import plot_cost_gaps_opt, plot_cost_gaps_bayesian, \
@@ -529,22 +530,52 @@ def get_proportion_sound_cost_bounds(analysis_info):
 
 def display_proportion_sound_cost_bounds(proportion_sound_cost_bonds_all_benchmarks):
 
+    column_benchmark_name = "Benchmark"
+    column_data_analysis_mode = "Analysis"
+    column_proportion_data_driven = "Data-driven"
+    column_proportion_hybrid = "Hybrid"
+
+    list_all_benchmark_names = list_benchmarks_data_driven_hybrid + \
+        list_benchmarks_data_driven
+    width_benchmark_name = max([len(column_benchmark_name)] + [len(name)
+                                                               for name in list_all_benchmark_names])
+    width_data_analysis_mode = max([len(column_data_analysis_mode)] + [len(name)
+                                                                       for name in ["Opt", "BayesWC", "BayesPC"]])
+    width_proportion = max(len(column_proportion_data_driven),
+                           len((column_proportion_hybrid)))
+    precision_proportion = 1
+
     def print_proportion_data_driven_data_analysis_mode(benchmark_name, data_analysis_mode, proportion):
         string_data_analysis_mode = get_string_data_analysis_mode(
             data_analysis_mode)
-        print("{:16} {:7} {:5.1f}%".format(
+        print("{:{width_benchmark_name}} {:{width_data_analysis_mode}} {:{width_proportion}.{precision_proportion}f}%".format(
             benchmark_name,
             string_data_analysis_mode,
-            100 * proportion[data_analysis_mode]))
+            100 * proportion[data_analysis_mode],
+            width_benchmark_name=width_benchmark_name,
+            width_data_analysis_mode=width_data_analysis_mode,
+            width_proportion=width_proportion-1,
+            precision_proportion=precision_proportion))
 
     def print_proportion_data_driven_hybrid_data_analysis_mode(benchmark_name, data_analysis_mode, proportion_data_driven, proportion_hybrid):
[…]

### 2024-03-08 benchmark_suite/toolbox/run_experiment.py

@@ -76,7 +76,6 @@ def run_all_benchmarks():
 
 
 if __name__ == "__main__":
-
     if sys.argv[1] == "all":
         run_all_benchmarks()
     else:

### 2024-03-08 README/step_by_step_instructions.tex
Explained in README the change in the analysis time of Hybrid RaML

@@
 %
-Firstly, \BayesWC{} and \BayesPC{} have higher percentages of sound cost bounds
-than \Opt{} (in both data-driven and hybrid resource analysis).
+Firstly, in both data-driven and hybrid resource analysis, \BayesWC{} and
+\BayesPC{} have higher percentages of sound cost bounds than \Opt{}.
 %
@@
 \end{verbatim}
+
+The table of analysis time produced by the artifact looks different from the one
+in the submitted version of the paper, in terms of both the numbers and layout.
+%
+This is because, since the submission, we have changed the configuration of
+sampling-based Bayesian inference algorithms and rerun experiments.
+%
+In the camera ready version of the paper, we will update the analysis time in
+Table~1.
 

### 2024-03-08 README/what_is_included.tex
Added a list of items necessary for artifact evaluation reviewers

% !TeX root = README.tex

\section{What is Included}

From Zenodo, you should obtain the following items:
\begin{itemize}
  \item This \texttt{README.pdf} document
  \item Archived and compressed Docker image \texttt{hybrid\_aara.tar.gz}
  \item Update version of the paper \texttt{paper.pdf}.
\end{itemize}

### 2024-03-09 README/step_by_step_instructions.tex
typo

@@
 In the Docker container, the \texttt{bin} directory of each benchmark already
-contains the experiment results that we reported in the paper.
+contains the experimental results that we reported in the paper.
 %
-We will demonstrate how to generate the experiment results from scratch in
+We will demonstrate how to generate the experimental results from scratch in
 \cref{sec:generate experiment results}.

### 2024-03-09 README/getting_started_guide.tex
Added README.md to the repository
minor typos; moved the note aboutchanges in the experiments

@@
 
-Our artifact, dubbed Hybrid Resource-Aware ML (RaML), is a program analysis tool
+Our artifact, dubbed Hybrid Resource-Aware ML (Hybrid RaML), is a program analysis tool
 that takes in an OCaml program and infers its worst-case polynomial cost bound
@@
 \end{verbatim}
+%
+It creates a Docker conainer (i.e., a runnable instance of the Docker image) and
+starts a shell inside the container.
 %
@@
   2.03295*M} is the average of its posterior distribution.
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "README"
+%%% End:

### 2024-03-09 README/step_by_step_instructions.tex
minor typos; moved the note aboutchanges in the experiments

@@
 
-\subsection{Display Experiment Results}
+\subsection{Display Experimental Results}
 \label{sec:display experiment results}
@@
 In this section, we demonstrate how to produce tables and plots in the paper
-from the experiment results that are stored in each benchmark's \texttt{bin}
+from the experimental results that are stored in each benchmark's \texttt{bin}
 directory.
@@
 \cref{sec:generate experiment results}.
-
-The tables and plots produced by the artifact are different from the ones in the
-submitted version of the paper.
-%
-This is because, since the submission, we have adjusted the hyperparameters for
-\BayesWC{} and \BayesPC{} in order to an automatic procedure for choosing
-hyperparameters.
-%
-The updated experiments results still preserve our key claims in Section~7 of
-the paper.
-%
-The updated version of the paper accompanies the artifact.
 
@@
 
-\subsection{Generate Experiment Results}
+\subsection{Generate Experimental Results}
 \label{sec:generate experiment results}
@@
 
-To view the updated tables and plots of the new experiment results, follow the
+To view the updated tables and plots of the new experimental results, follow the
 steps in \cref{sec:display experiment results}.
 %
-The experiment results for (Data-Driven and Hybrid) \BayesWC{} and \BayesPC{}
+The experimental results for (Data-Driven and Hybrid) \BayesWC{} and \BayesPC{}
 after rerunning the experiments may look different from the tables and plots
@@
 \end{verbatim}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "README"
+%%% End:

### 2024-03-09 README/what_is_included.tex
typo
minor typos; moved the note aboutchanges in the experiments

@@
   \item Archived and compressed Docker image \texttt{hybrid\_aara.tar.gz}
-  \item Update version of the paper \texttt{paper.pdf}.
+  \item Updated version of the paper \texttt{paper.pdf}.
 \end{itemize}
+
+\emph{\textbf{Note:} The tables and plots produced by the artifact are
+  slightly different from the ones in the submitted version of the
+  paper.
+%
+  This is because, since the submission, we have adjusted the
+  hyperparameters for \BayesWC{} and \BayesPC{} using an automatic
+  procedure for choosing hyperparameters.
+%
+  The updated experiments results still preserve all key findings in
+  Section~7 of the paper.
+%
+  The updated version of the paper accompanies the artifact.}

### 2024-03-09 README/getting_started_guide.tex
Explain the configuration files for Hybrid RaML

@@
 using the technique Hybrid AARA described in the paper.
+%
+Hybrid AARA integrates data-driven resource analysis (i.e., inferring a cost
+bound from the runtime cost measurements of the program) and static resource
+analysis (i.e., inferring a cost bound from the source code of the program).
 
@@
 
-The initial working directory \texttt{playground} has a file \texttt{append.ml},
-which stores an OCaml function \texttt{append}.
+\subsection{Example Program}
+
+The initial working directory \texttt{playground} has a file \texttt{append.ml}.
 %
-Given two inputs lists, the \texttt{append} function appends the first input to
+It stores (i) an OCaml function \texttt{append} and (ii) inputs to the function
+\texttt{append} for generating runtime cost measurements.
+%
+To view the function \texttt{append}'s source code, run
+\begin{verbatim}
+# cat append.ml | head -16
+\end{verbatim}
+
+Given two inputs lists, the function \texttt{append} appends the first input to
 the second one.
 %
-For each element in the first input that the function processes, it incurs a
-cost ranging from 0.5 to 1.0.
+For each element in the first input processed by the function, it incurs a cost
+ranging from 0.5 to 1.0 (indicated by a code annotation \texttt{Raml.tick}).
 %
-Therefore, the worst-case cost bound of the function is $1.0 \cdot M$, where $M$
+Therefore, the worst-case cost bound of the function \texttt{append} is $1.0 \cdot M$, where $M$
 is the length of the first input list.
+
+Our goal is to infer a sound worst-case bound of the function \texttt{append} by
+Hybrid AARA, which integrates data-driven and static resource analyses.
+%
+The stepping function \texttt{step\_function} called inside function
+\texttt{append} is enclosed by a code annotation \texttt{Raml.stat}.
+%
+This annotation indicates we perform data-driven resource analysis on the
+stepping function---the rest of \texttt{append}'s source code is analyzed by
+static resource analysis.
+%
+To perform data-driven analysis, Hybrid AARA first runs the function
+\texttt{append} and collect runtime cost measurements of the stepping function
+\texttt{step\_function}.
+%
+The inputs to \texttt{append} used for generating runtime cost measurements are
+stored in the second half of the file \texttt{append.ml}.
+%
+To view these inputs, run
+\begin{verbatim}
+# cat append.ml | tail -74
+\end{verbatim}
+%
+In our case, we have chosen inputs in such a way that (i) the input sizes grow
+exponentially and (ii) the values of list elements are chosen randomly.
 
@@
 resource analysis: Hybrid \Opt{}, Hybrid \BayesWC{}, and Hybrid \BayesPC{}.
+%
+Although the paper also describes purely data-driven resource analysis, which is
+a special case of hybrid resource analysis, this Getting Started Guide focuses
+on hybrid resource analysis of the function \texttt{append}.
 
@@
 
+Hybrid \Opt{} uses \underline{opt}imization, specifically linear programming,
+for the data-driven part of resource analysis.
+%
 To perform Hybrid \Opt{} on the \texttt{append} function, run
@@
 
-Next, to perform Hybrid \BayesWC{}, run
+Hybrid \BayesWC{} conducts \underline{Bayes}ian inference on
+\underline{w}orst-case \underline{c}osts for the data-driven part of resource
+analysis.
+%
+To perform Hybrid \BayesWC{}, run
 \begin{verbatim}
@@
 
+Hybrid \BayesPC{} conducts \underline{Bayes}ian inference on
+\underline{p}olynomial \underline{c}oefficients for the data-driven part of
+resource analysis.
+%
 To perform Hybrid \BayesPC{}, run
@@
 
+\subsection{Configuration Files}
+
+Configuration files supplied to Hybrid RaML specify hyperparameters for
+linear programming and Bayesian inference.
+
+In the configuration file \texttt{config\_opt.json} for \Opt{},
+\texttt{cost\_gaps\_optimization} inside set to true, and
+\texttt{coefficients\_optimization} is set to \texttt{Equal\_weights}.
+%
+The first setting means we optimize not only the coefficients of an overall cost
+bound but also the cost gaps (i.e., the gaps between the predicted costs and
+observed costs).
+%
+The second setting means we assign equal weights to all coefficients in an
+overall cost bound regardless of their degrees.
+
+The configuration file \texttt{config\_bayeswc.json} for \BayesWC{} specifies
+(i) the probabilistic model hyperparameters $\beta$ and $s$ in Weibull survival
+analysis\footnote{Explained in this PyMC tutorial:
+  \url{https://www.pymc.io/projects/examples/en/2022.12.0/survival_analysis/bayes_param_survival_pymc3.html}}
+and (ii) the inference hyperparameters such as the number of chains and the
+number of iterations to run in a sampling-based Bayesian inference algorithm.
+
+The configuration file \texttt{config\_bayespc.json} for \BayesPC{} contains (i)
+the probabilistic model hyperparameters for Gaussian and Weibull distributions
+and (ii) the inference hyperparameters for reflective Hamiltonian Monte Carlo
+(HMC) used in \BayesWC{}.
+%
+Reflective HMC runs a sampling-based Bayesian inference algorithm within a
+feasible region of a linear program.
+
 %%% Local Variables:

### 2024-03-09 README/step_by_step_instructions.tex
Explain the configuration files for Hybrid RaML

@@
 in the paper.
-%
+
 The paper evaluates both purely data-driven resource analysis and hybrid
@@
 
-Inside the benchmark directory \texttt{/home/hybrid\_aara/benchmark\_suite},
+Inside the benchmark suite directory \texttt{/home/hybrid\_aara/benchmark\_suite},
 each benchmark has its own directory, which contains the following three
@@
 %
-In the camera ready version of the paper, we will update the analysis time in
+In the camera-ready version of the paper, we will update the analysis time in
 Table~1.
@@
 
-To perform Hybrid AARA on the benchmark \texttt{QuickSort} using purely
-data-driven resource analysis, run
+For example, to perform Hybrid AARA on the benchmark \texttt{QuickSort} using
+purely data-driven resource analysis, run
 \begin{verbatim}
@@
 %
-It will run Data-Driven \Opt{}, Data-Driven \BayesWC{}, and Data-Driven
-\BayesPC{}.
+It runs Data-Driven \Opt{}, Data-Driven \BayesWC{}, and Data-Driven \BayesPC{}.
 %
@@
 %
-It will run Hybrid \Opt{}, Hybrid \BayesWC{}, and Hybrid \BayesPC{}.
+It runs Hybrid \Opt{}, Hybrid \BayesWC{}, and Hybrid \BayesPC{}.
 %
@@
 RaML (in OCaml), (ii) the volesti-RaML interface (in C++), and (iii) the
-benchmark suite (in Python).
+execution and analysis of benchmark suite (in Python).
 %
@@
 
-The project directory inside the image contains two additional directories.
+The project directory contains two additional directories.
 %

### 2024-03-11 README/what_is_included.tex
Added a pointer to Appendix C in the paper about automatically choosing hyperparameters

@@
 
-\emph{\textbf{Note:} The tables and plots produced by the artifact are
-  slightly different from the ones in the submitted version of the
-  paper.
+\emph{\textbf{Note:} The tables and plots produced by the artifact are slightly
+  different from the ones in the submitted version of the paper.
   %
-  This is because, since the submission, we have adjusted the
-  hyperparameters for \BayesWC{} and \BayesPC{} using an automatic
-  procedure for choosing hyperparameters.
+  This is because, since the submission, we have adjusted the hyperparameters
+  for \BayesWC{} and \BayesPC{} using an automatic procedure for choosing
+  hyperparameters (Appendix~C of the paper).
   %
-  The updated experiments results still preserve all key findings in
-  Section~7 of the paper.
+  The updated experiments results still preserve all key findings in Section~7
+  of the paper.
   %

### 2024-03-11 README/what_is_included.tex
Minor revision

--- 2024-03-09 README/what_is_included.tex
@@
 
-\emph{\textbf{Note:} The tables and plots produced by the artifact are
-  slightly different from the ones in the submitted version of the
-  paper.
+\emph{\textbf{Note:} The tables and plots produced by the artifact are slightly
+  different from the ones in the submitted version of the paper.
   %
-  This is because, since the submission, we have adjusted the
-  hyperparameters for \BayesWC{} and \BayesPC{} using an automatic
-  procedure for choosing hyperparameters.
+  This is because, since the submission, we have adjusted the hyperparameters
+  for \BayesWC{} and \BayesPC{} using an automatic procedure for choosing
+  hyperparameters (Appendix~C of the paper), as requested by the paper
+  reviewers.
   %
-  The updated experiments results still preserve all key findings in
-  Section~7 of the paper.
+  The updated experiments results still preserve all key findings in Section~7
+  of the paper.
   %

### 2024-03-11 README/getting_started_guide.tex
Added a warning that macOS may change the name of the Docker image after loading

@@
 
-Load and run the Docker image as follows:
+Load a Docker image by running
 \begin{verbatim}
 $ docker load --input hybrid_aara.tar.gz
+\end{verbatim}
+%
+It creates an image named \texttt{hybrid\_aara} and stores it locally on your
+machine.
+%
+On some platforms (e.g., macOS), Docker may create an image with a slightly
+different name from \texttt{hybrid\_aara}.
+%
+You can check the name of the image by running \verb|$ docker ps|, which will
+display a list of images on your local machine.
+
+To run the image \texttt{hybrid\_aara}, run
+\begin{verbatim}
 $ docker run --name hybrid_aara -it --rm hybrid_aara
@@
 %
-It creates a Docker conainer (i.e., a runnable instance of the Docker image) and
-starts a shell inside the container.
-%
+It creates a Docker container (i.e., a runnable instance of the Docker image)
+named \texttt{hybrid\_aara} and starts a shell inside the container.
+
 Throughout this document, any command line starting with \texttt{\#} is executed
@@
 %
-Although the paper also describes purely data-driven resource analysis, which is
-a special case of hybrid resource analysis, this Getting Started Guide focuses
-on hybrid resource analysis of the function \texttt{append}.
+Although the paper also describes purely data-driven resource analysis
+(Section~5), which is a special case of hybrid resource analysis, this Getting
+Started Guide focuses on hybrid resource analysis of the function
+\texttt{append}.
 

### 2024-03-11 README/step_by_step_instructions.tex
Added a warning that macOS may change the name of the Docker image after loading

@@
 %
-Nonetheless, there should not be any significant deviation.
+Nonetheless, there should not be any significant deviation from the results
+reported in the paper.
 
@@
 
-The project directory contains two additional directories.
+The project directory contains two additional directories that come from other
+sources.
 %
@@
 
-The code for building a Docker image is publicly available on GitHub:
+The code for building a Docker image is available on GitHub:
 \url{https://github.com/LongPham7/hybrid_aara_artifact}.
@@
 %
-It will take 20--30 minutes.
+We need a period at the end of the command to indciate that Dockerfile exists in
+the current working directory.
+%
+The build will take 20--30 minutes.
 %
@@
 machine.
-%
-To run this image after it is built, run
+
+To run the image \texttt{hybrid\_aara}, run
 \begin{verbatim}

### 2024-03-11 README/getting_started_guide.tex
Updated the explanation of hyperparameters

@@
 that takes in an OCaml program and infers its worst-case polynomial cost bound
-using the technique Hybrid AARA described in the paper.
+using the technique Hybrid AARA developed in the paper.
 %
@@
 The configuration file \texttt{config\_bayeswc.json} for \BayesWC{} specifies
-(i) the probabilistic model hyperparameters $\beta$ and $s$ in Weibull survival
-analysis\footnote{Explained in this PyMC tutorial:
-  \url{https://www.pymc.io/projects/examples/en/2022.12.0/survival_analysis/bayes_param_survival_pymc3.html}}
+(i) the probabilistic model hyperparameter $\gamma_0$ in Weibull survival
+analysis\footnote{See Appendix~C of the updated version of the paper. The
+probabilistic model is also explained in this PyMC tutorial:
+\url{https://www.pymc.io/projects/examples/en/2022.12.0/survival_analysis/bayes_param_survival_pymc3.html}.}
 and (ii) the inference hyperparameters such as the number of chains and the
@@
 The configuration file \texttt{config\_bayespc.json} for \BayesPC{} contains (i)
-the probabilistic model hyperparameters for Gaussian and Weibull distributions
-and (ii) the inference hyperparameters for reflective Hamiltonian Monte Carlo
-(HMC) used in \BayesWC{}.
+the probabilistic model hyperparameters $\gamma_0$ for normal prior
+distributions and $\theta_0, \theta_1$ for Weibull prior distributions and (ii)
+the inference hyperparameters for reflective Hamiltonian Monte Carlo (HMC) used
+in \BayesPC{}.
 %

### 2024-03-29 reviews/response_reound1.md
Added a review and response

Thank you all for the feedback.

# Review A

Thank you for taking the time to run all Python scripts. We are happy that you
did not encounter any technical issues with the artifact.

# Review B

Thank you for going through the getting-started guide. We are happy that you did
not encounter any technical issues with the artifact.

# Review C

> The binary included in the docker image crashes immediately (Illegal
> instruction (core dumped)) on my architecture (described below to ease
> debugging).

Thank you for reporting this issue. We suspect that the Docker container
requires an instruction that your computer does not support. We built the docker
image on the OS Ubuntu 22.04 LTS and the CPU Intel(R) Core(TM) i7-7600U CPU @
2.80GHz.

We could not identify the root cause of the issue. So could you please run the
artifact by cloning the GitHub repository and building a Docker image locally on
your machine? We are happy that at least you successfully built the image on
your machine.

> It would be good to add instructions in the README to recompile the code
> directly inside the docker, and avoid those crashes. This would additionally
> allow user to tweak the code directly inside the docker, and observe changes
> there.

Thank you for the suggestion. Technically, from the Dockerfile in the GitHub
repository, one can learn how to recompile the code inside the Docker container.

In the revision of `README.pdf`, we will provide details on how to recompile (i)
the C++ code of the volesti-RaML interface and (i) the OCaml code of Hybrid
RaML. The remaining code, such as the Python scripts, does not need
recompilation after modification.

> Being able to test to analyser on new benchmarks is required to grant the
> "Reusable" badge. It would be helpful to add a small paragraph in the README
> instructing how to do so, and include tools in the docker image to make this
> process easier.

If the user wishes to analyze their custom OCaml program using Hybrid RaML, the
user should first prepare (i) the source file of their OCaml program, augmented
with a list of inputs for runtime cost data generation and (ii) a configuration
file specifying hyperparameters of Hybrid AARA. To learn the formats of these
files, the user can look at the examples inside the artifact. Finally, The user
runs Hybrid RaML as demonstrated in Section 1 of `README.pdf`.

We will explain this point in the revision of `README.pdf`.

> It would improve the artifact to include an editor.

We will install the text editor Vim in the updated Docker image. Alternatively,
if the user wishes to install a different text editor, while the Docker
container is running, the user can run `apt update && apt install <editor-name>
-y` inside the container.

> Should input_dataset be entered manually by the users on each new benchmark?
> Are scripts provided to generate them automatically?

The artifact already comes with a Python script (`input_data_generation.py`
inside the directory `home/hybrid_aara/benchmark_suite/toolbox/`) for generating
lists, pairs of lists (for the benchmark MapAppend), and nested lists (for the
benchmark Concat). For example, the function `create_exponential_lists` inside
this script generates lists whose sizes grow exponentially (e.g., 1, 2, 4, 8,
16, etc.). Here, the initial size (i.e., 1) and exponent (i.e., 2) are specified
by the user. The content of each list is determined randomly. The function
`convert_lists_python_to_ocaml` then converts a list from the Python format to
the OCaml format.

We will mention this Python script in the revised `README.pdf`. Also, we will
revise the script such that, when the user runs `python3
input_data_generation.py`, the script prints out an example collection of input
lists used for runtime cost data generation.

### 2024-03-29 benchmark_suite/toolbox/input_data_generation.py

@@ -1,5 +1,6 @@
 import random
 
+
 # Create a random list
 
 
@@ -12,10 +13,12 @@ def create_random_list(max_size, max_achieved=False):
 
     max_element_size = max_size
 
-    # We randomly sample list elements without replacement.
-    # We don't allow replacement so that the complexity analysis of median of medians works.
+    # We randomly sample list elements without replacement. We don't allow
+    # replacement so that the complexity analysis of the median-of-medians-based
+    # linear-time selection algorithm works.
     return random.sample(list(range(0, max_element_size)), list_length)
     # return random.choices(list(range(1, max_element_size+1)), k=list_length)
+
 
 # Create lists.
 
@@ -58,7 +61,8 @@ def create_input_data_lists(input_data_generation_params):
         raise Exception("The given input size distribution is invalid.")
     return input_data_python
 
-# Create pairs of lists. This is used in the benchmark append.
+
+# Create pairs of lists. This is used in the benchmark MapAppend.
 
 
 def create_random_pairs_lists(num_samples, max_input_size1, max_input_size2):
@@ -111,10 +115,11 @@ def create_input_data_pairs_lists(input_data_generation_params):
         raise Exception("The given input size distribution is invalid.")
     return input_data_python
 
-# Create nested lists. This is used in the benchmark concat.
+
+# Create nested lists. This is used in the benchmark Concat.
 
 
-def create_random_nested_list(max_num_inner_lists, max_inner_list_size, max_num_inner_lists_achieved=False, max_inner_list_size_achieved=False):
+def create_random_nested_list(max_num_inner_lists, max_inner_list_size, max_num_inner_lists_achieved=False):
     if (max_num_inner_lists == 0 or max_num_inner_lists_achieved):
         num_inner_lists = max_num_inner_lists
     else:
@@ -182,6 +187,7 @@ def create_input_data_nested_lists(input_data_generation_params):
         raise Exception("The given input size distribution is invalid.")
     return input_data_python
 
+
 # Convert a list from Python to OCaml
 
 
@@ -193,6 +199,7 @@ def convert_list_python_to_ocaml(list_python):
         else:
             list_ocaml += "; " + str(element)
     return list_ocaml + "]"
+
 
 # Convert input data of lists from Python to OCaml
 
@@ -209,6 +216,7 @@ def convert_lists_python_to_ocaml(input_data_python, split_line=True):
             else:
[…]

### 2024-03-29 reviews/response_reound1.md
Revised README according to the feedback

@@
 
-In the revision of `README.pdf`, we will provide details on how to recompile (i)
-the C++ code of the volesti-RaML interface and (i) the OCaml code of Hybrid
-RaML. The remaining code, such as the Python scripts, does not need
+In Section 4.4 of the revised `README.pdf`, we provide details on how to
+recompile (i) the C++ code of the volesti-RaML interface and (i) the OCaml code
+of Hybrid RaML. The remaining code, such as the Python scripts, does not need
 recompilation after modification.
@@
 user should first prepare (i) the source file of their OCaml program, augmented
-with a list of inputs for runtime cost data generation and (ii) a configuration
-file specifying hyperparameters of Hybrid AARA. To learn the formats of these
-files, the user can look at the examples inside the artifact. Finally, The user
-runs Hybrid RaML as demonstrated in Section 1 of `README.pdf`.
+with a collection of inputs for generating runtime cost data and (ii) a
+configuration file specifying hyperparameters of Hybrid AARA. To learn the
+formats of these files, the user can look at the examples inside the artifact.
+Finally, The user runs Hybrid RaML as demonstrated in Section 1 of `README.pdf`.
 
-We will explain this point in the revision of `README.pdf`.
+In Section 4.3 of the revised `README.pdf`, we explain this point.
 
@@
 
-We will mention this Python script in the revised `README.pdf`. Also, we will
-revise the script such that, when the user runs `python3
+In Section 4.3 of the revised `README.pdf`, we mention this Python script. Also,
+we will revise the script such that, when the user runs `python3
 input_data_generation.py`, the script prints out an example collection of input

### 2024-03-29 README/build_and_customize.tex
Revised README according to the feedback

% !TeX root = README.tex

\section{Build and Customize the Artifact}

This section describes how to build and customize Hybrid RaML.

\subsection{Source Code}
\label{sec:Source Code}

Our artifact contains three tools that we have built by ourselves: (i) Hybrid
RaML (in OCaml), (ii) the volesti-RaML interface (in C++), and (iii) the
execution and analysis of benchmark suite (in Python).
%
Their source code is stored in directories \texttt{raml},
\texttt{volesti\_raml\_interface}, and \texttt{benchmark\_suite} inside the
project directory \texttt{/home/hybrid\_aara} in the Docker image.

The project directory contains two additional directories that come from other
sources.
%
The third-party C++ library volesti\footnote{Available here:
  \url{https://github.com/GeomScale/volesti}.} is stored in the directory
\texttt{volesti}.
%
The linear-program solver COIN-OR CLP\footnote{Available here:
  \url{https://github.com/coin-or/Clp}.} is stored in the directory \texttt{clp}.

\subsection{Build the Docker Image}

The code for building a Docker image is available on GitHub:
\url{https://github.com/LongPham7/hybrid_aara_artifact}.
%
To build a Docker image, clone the GitHub repository and then run (in the root
directory)
\begin{verbatim}
$ docker build -t hybrid_aara .
\end{verbatim}
%
We need a period at the end of the command to indciate that \texttt{Dockerfile}
exists in the current working directory.
%
The build will take 20--30 minutes.
%
The resulting image is named \texttt{hybrid\_aara} and is stored locally on your
machine.

To run the image \texttt{hybrid\_aara}, run
\begin{verbatim}
$ docker run --name hybrid_aara -it --rm hybrid_aara
\end{verbatim}
%
It creates and runs a Docker container with the same name \texttt{hybrid\_aara}.
%
If you want to save the image as a tar archive and compress it, run
\begin{verbatim}
$ docker save hybrid_aara | gzip > hybrid_aara.tar.gz
\end{verbatim}

\subsection{Test Custom Input OCaml Programs}

Suppose we want to analyze a custom OCaml function $f$ using Hybrid AARA.
%
We first prepare two files: (i) an OCaml source file and (ii) a JSON
configuration file.

The OCaml source file stores (i) the OCaml code of the function $f$ (and
possibly other auxiliary functions) and (ii) the OCaml code to be executed in
order to collect runtime cost samples of the function $f$.
%
For example, in the file \texttt{append.ml} described in \cref{sec:Example
  Program}, the OCaml code used for generating runtime cost data has the form
\begin{verbatim}
let input_dataset = [([31; 11; 26; 25], [10; 36; 20; 24]); ...] in
map input_dataset (fun (x, y) -> append x y)
\end{verbatim}
%
This code first creates a list of inputs (i.e. pairs of integer lists) to the
function \texttt{append} and then runs the function on every input.
%
During its execution, whenever we encounter an annotated code fragment
\texttt{Raml.stat(...)}, we record its runtime sample, namely the input, output,
and cost.
%
We aggregate all runtime cost samples into a dataset, which will later be used
in data-driven resource analysis.

For convenience, our artifact comes with a Python script for generating a
collection of inputs for OCaml programs.
%
The file \texttt{input\_data\_generation.py} inside the directory
\texttt{/home/hybrid\_aara/benchmark\_suite/toolbox}
contains a function \texttt{create\_exponential\_lists}, which creates a
collection of integer lists whose sizes grow exponentially (e.g., 1, 2, 4, 8,
etc.).
%
The content of each integer list is chosen randomly.
%
The function \texttt{convert\_list\_python\_to\_ocaml} then converts integer
lists from the Python format to the OCaml format.
%
To see an example, in the directory
\texttt{/home/hybrid\_aara/benchmark\_suite/toolbox}, run
\begin{verbatim}
# python3 input_data_generation.py
\end{verbatim}
%
It prints out a collection of lists whose sizes grow exponentially.

Finally, the JSON configuration file specifies hyperparameters of Hybrid AARA.
%
To learn its syntax, you can take a look at the file \texttt{config.json} inside
each benchmark's \texttt{bin} directory.

\subsection{Modify and Compile Source Code inside the Docker Container}

To modify files inside the Docker container while it runs, we can use the text
editor Vim.
%
If you wish to use a different text editor, modify \texttt{Dockerfile} in the
GitHub repository and rebuild the artifact as instructed in \cref{sec:Source
Code}.
%
Alternatively, while the Docker container runs, you can install the text
editor by
\begin{verbatim}
# apt update && apt install <text-editor> -y
\end{verbatim}

To recompile code \emph{inside} the Docker container after the code has been
modified, follow these steps.
%
For the OCaml source code of Hybrid RaML, go to the directory
\texttt{/home/hybrid\_aara/raml} and then run
\begin{verbatim}
# eval $(opam env)
# make
\end{verbatim}
%
The first line, which initializes OCaml-related environment variables, is only
necessary the first time you recompile Hybrid RaML's source code.

To compile the C++ source code of the volesti-RaML interface, go to the
directory \texttt{/home/hybrid\_aara/volesti\_raml\_interface/bin} and then run
\begin{verbatim}
# cmake .. && cmake --build .
\end{verbatim}

All the other code in the artifact, such as Python scripts inside the benchmark
suite, does not require recompilation after modification.

### 2024-03-29 README/getting_started_guide.tex
Fixed a typo
Revised README according to the feedback

@@
 It creates an image named \texttt{hybrid\_aara} and stores it locally on your
-machine.
 %
-On some platforms (e.g., macOS), Docker may create an image with a slightly
-different name from \texttt{hybrid\_aara}.
+Docker may create an image with a slightly different name from
+\texttt{hybrid\_aara}.
 %
-You can check the name of the image by running \verb|$ docker ps|, which will
-display a list of images on your local machine.
+You can check the name of the image by running \verb|$ docker images|, which
+will display a list of images on your local machine.
 
@@
 \subsection{Example Program}
+\label{sec:Example Program}
 
@@
 (i) the probabilistic model hyperparameter $\gamma_0$ in Weibull survival
-analysis\footnote{See Appendix~C of the updated version of the paper. The
+analysis\footnote{See Appendix~B of the updated version of the paper. The
   probabilistic model is also explained in this PyMC tutorial:

### 2024-03-29 README/step_by_step_instructions.tex
Updated the explanation of hyperparameters
Revised README according to the feedback

@@
 %
-This is because, since the submission, we have changed the configuration of
-sampling-based Bayesian inference algorithms and rerun experiments.
+This is because, since the submission, we have changed the hyperparameters of
+Bayesian inference and rerun experiments.
 %
@@
 
-For example, to perform Hybrid AARA on the benchmark \texttt{QuickSort} using
-purely data-driven resource analysis, run
+For example, to perform Data-Driven \Opt{} on the benchmark \texttt{QuickSort},
+run
+\begin{verbatim}
+# # python3 run_experiment.py QuickSort data_driven opt
+\end{verbatim}
+%
+The analysis should finish in 15 seconds.
+%
+To perform all data-driven resource analyses on the benchmark
+\texttt{QuickSort}, run
 \begin{verbatim}
@@
 %
-If we instead want to perform hybrid resource analysis,
+If we instead want to perform all hybrid resource analyses, replace
+\texttt{data\_driven} with \texttt{hybrid}:
 \begin{verbatim}
@@
 
-\subsection{Source Code}
-
-Our artifact contains three tools that we have built by ourselves: (i) Hybrid
-RaML (in OCaml), (ii) the volesti-RaML interface (in C++), and (iii) the
-execution and analysis of benchmark suite (in Python).
-%
-Their source code is stored in directories \texttt{raml},
-\texttt{volesti\_raml\_interface}, and \texttt{benchmark\_suite} inside the
-project directory \texttt{/home/hybrid\_aara} in the Docker image.
-
-The project directory contains two additional directories that come from other
-sources.
-%
-The third-party C++ library volesti\footnote{Available here:
-  \url{https://github.com/GeomScale/volesti}.} is stored in the directory
-\texttt{volesti}.
-%
-The linear-program solver COIN-OR CLP\footnote{Available here:
-  \url{https://github.com/coin-or/Clp}.} is stored in the directory \texttt{clp}.
-
-The code for building a Docker image is available on GitHub:
-\url{https://github.com/LongPham7/hybrid_aara_artifact}.
-%
-To build a Docker image, clone the GitHub repository and then run (in the root
-directory)
-\begin{verbatim}
-$ docker build -t hybrid_aara .
-\end{verbatim}
-%
-We need a period at the end of the command to indciate that Dockerfile exists in
-the current working directory.
-%
-The build will take 20--30 minutes.
-%
-The resulting image is named \texttt{hybrid\_aara} and is stored locally on your
-machine.
-
-To run the image \texttt{hybrid\_aara}, run
-\begin{verbatim}
-$ docker run --name hybrid_aara -it --rm hybrid_aara
-\end{verbatim}
-%
-If you want to save the image as a tar archive and compress it, run
-\begin{verbatim}
-$ docker save hybrid_aara | gzip > hybrid_aara.tar.gz
-\end{verbatim}
-
 %%% Local Variables:

### 2024-03-29 README/what_is_included.tex
Revised README according to the feedback

--- 2024-03-09 README/what_is_included.tex
@@
 
-\emph{\textbf{Note:} The tables and plots produced by the artifact are
-  slightly different from the ones in the submitted version of the
-  paper.
+\emph{\textbf{Note:} The tables and plots produced by the artifact are slightly
+  different from the ones in the submitted version of the paper.
   %
-  This is because, since the submission, we have adjusted the
-  hyperparameters for \BayesWC{} and \BayesPC{} using an automatic
-  procedure for choosing hyperparameters.
+  This is because, since the submission, we have adjusted the hyperparameters
+  for \BayesWC{} and \BayesPC{} using an automatic procedure for choosing
+  hyperparameters (Appendix~B of the paper), as requested by the paper
+  reviewers.
   %
-  The updated experiments results still preserve all key findings in
-  Section~7 of the paper.
+  The updated experiments results still preserve all key findings in Section~7
+  of the paper.
   %

### 2024-03-29 README/getting_started_guide.tex
Minor refactoring

@@
 %
-You can check the name of the image by running \verb|$ docker images|, which
-will display a list of images on your local machine.
+To check the name of the image, display all Docker images on your local machine
+by running
+\begin{verbatim}
+$ docker images
+\end{verbatim}
 
@@
 named \texttt{hybrid\_aara} and starts a shell inside the container.
+%
+If the command does not run properly, you can instead build the image locally on
+your machine as instructed in \cref{sec:Build the Docker Image}.
 

### 2024-03-30 reviews/response_reound1.md
Minor refactoring
Update response_reound1.md

@@
 
+In Section 2 of the revised `README.pdf`, we refer the reader to Section 4.2 if
+they have trouble running the prebuilt image.
+
 > It would be good to add instructions in the README to recompile the code
@@
 
-Thank you for the suggestion. Technically, from the Dockerfile in the GitHub
-repository, one can learn how to recompile the code inside the Docker container.
+Thank you for the suggestion.
 
@@
 formats of these files, the user can look at the examples inside the artifact.
-Finally, The user runs Hybrid RaML as demonstrated in Section 1 of `README.pdf`.
+Finally, the user runs Hybrid RaML as demonstrated in Section 1 of `README.pdf`.
 

### 2024-03-31 reviews/response_reound1.md
Revised our response to the technical issue with Docker

@@
 
-Thank you for reporting this issue. We suspect that the Docker container
-requires an instruction that your computer does not support. We built the docker
-image on the OS Ubuntu 22.04 LTS and the CPU Intel(R) Core(TM) i7-7600U CPU @
-2.80GHz.
+Thank you for reporting this issue. The same error message has been reported in
+other Docker images (e.g.,
+[here](https://github.com/ultralytics/ultralytics/issues/7085)). We suspect that
+the prebuilt Docker image requires an instruction that your computer does not
+support. We built the Docker image on the OS Ubuntu 22.04 LTS and the CPU
+Intel(R) Core(TM) i7-7600U CPU @ 2.80GHz. We also tested the prebuilt image on
+macOS with Apple silicon, and it ran successfully.
 
-We could not identify the root cause of the issue. So could you please run the
-artifact by cloning the GitHub repository and building a Docker image locally on
-your machine? We are happy that at least you successfully built the image on
-your machine.
+We could not identify the root cause of the issue. We believe it is a technical
+issue of Docker, rather than our code. As stated on the website of PLDI 2024
+Artifact Evaluation, it is recommended to provide prebuilt Docker images (or
+VMs), instead of providing scripts for building them. Hence, we will keep the
+artifact in the form of a prebuilt Docker image, even though it is not
+self-contained anymore if the user has trouble with the prebuilt image.
+
+If you do not mind, could you please run the artifact by cloning the GitHub
+repository and building a Docker image locally on your machine? We are happy
+that at least you successfully built the image on your machine.
 
@@
 
-In Section 4.4 of the revised `README.pdf`, we provide details on how to
+In Section 4.4 of the revised `README.pdf`, we provide details of how to
 recompile (i) the C++ code of the volesti-RaML interface and (i) the OCaml code

### 2024-04-05 README/build_and_customize.tex
Minor refactoring
Fixed a typo in README.pdf and added the updated review C

@@
 \subsection{Build the Docker Image}
+\label{sec:Build the Docker Image}
 
@@
 To compile the C++ source code of the volesti-RaML interface, go to the
-directory \texttt{/home/hybrid\_aara/volesti\_raml\_interface/bin} and then run
+directory \texttt{/home/hybrid\_aara/volesti\_raml\_interface/build} and then
+run
 \begin{verbatim}
